---
title: YOUR MANUSCRIPT TITLE
subtitle: YOUR MANUSCRIPT SUBTITLE
date: last-modified
date-format: |
    | DD MMMM YYYY
authors:
  - name: YOUR NAME
    email: your.email@example.com
    orcid: 0000-0000-0000-0000
    affiliations:
      - ref: uni
    correspondence: true
affiliations:
  - id: uni
    name: Your University Name
execute:
  echo: false
  warning: false
  error: false
  message: false
format:
  orcid-pdf:
    number-sections: true
    # include-in-header:
    #   - text: |
          #
# bibliography: references.bib
# csl: extra/apa.csl
abstract: |
  YOUR ABSTRACT GOES HERE. The abstract should be a single paragraph of no more than 250 words that summarizes the main findings and contributions of your manuscript.
keywords: British Politics, Referendum, Brexit
---

# Introduction

YOUR INTRODUCTION GOES HERE. The introduction should provide background information on the topic, state the research question, and outline the structure of the manuscript.

# Descriptive Analysis

```{r}
library(here)
library(tidyverse)
i_am("manuscript/manuscript.qmd") # helps with relative paths
```

YOUR DESCRIPTIVE ANALYSIS GOES HERE. This section should present the main descriptive statistics and visualizations that summarize the data.

@fig-turnout shows the voter turnout by region in the 2016 Brexit referendum.

```{r}
#| fig-cap: "Voter turnout by region in the 2016 Brexit referendum."
#| fig-pos: "H"
#| label: fig-turnout
plot <- read_rds(here("outputs/turnout_by_region.rds"))
plot
```

# Results

@tbl-reg shows the regression results for the main analysis.

```{r}
#| label: tbl-reg
#| tbl-cap: "Regression results for the main analysis."
#| tbl-pos: H
reg_table <- read_rds("outputs/regression_table.rds")
reg_table
```